### 2016-07-01 appendix.tex
Final Version
Submitted to VLDB

\subsection{Proof of Theorem~\ref{THM:SPM_LB} and~\ref{THM:SPM_LB_INC}}
\label{apx:thm2proof}
\begin{proof}
$\Gamma$ can be formalized in a linear algebra way:
Let $G_A$ be an aggregated graph, with a $n \times n$ adjacent matrix $J$.
Since a vertex order is a permutation of $J$, the adjacent matrices 
of any reordered graphs can be represented as $PJP^T$
where $P \in \mathbb{P}$ is a $n\times n$ \emph{permutation matrix}~\footnote{an identity matrix with rows shuffled}.
In star partition, we assign each edge $e(i,j)$ in $G_A$ to the lower vertex, 
then the matrix $B=\triu(PJP^T)$~\footnote{\text{triu} is the upper triangle part of a matrix}
represents the assignment matrix wrt. $P$ (i.e., $b_{i,j} = 1$ if vertex $j$ is in star $Sr_i$).
Let vector $\vec{b}$ be the \textit{one}\footnote{every element in $\vec{b}$ is $1$} 
vector with size $n$. Let $\vec{c} = B\vec{b}$, then each $c_i$ 
denotes the number of edges in star $Sr_i$. Thus, $\Gamma$ can be represented
as the infinity norm of $B\vec{b}$. Let $\Gamma^*$ be the minimum $\Gamma$ among all vertex orders, that is

@@

Let $B^*$ be the assignment matrix wrt. the optimal vertex order.
Since we have a star for each object, by the degree-sum formula and pigeon-hole theorem, 
$\Gamma^*=||B^*\vec{b}||_\infty \geq d/2$.
Next, for a ordering $P$, let $e_{i,j}$ be an entry in $PAP^T$. Since 
edges in graph $G$ are independent, then $e_{i,j}$s are independent. 
Let $d_i$ denote the degree of vertex $i$, since ordering of vertex does not
affect the average degree,
then $E[d_i]=E[\Sigma_{1\leq j \leq n}e_{i,j}]=d$. Therefore, 
entries in $B$ can be written as :

@@

\begin{equation*}
\begin{split}
	Pr(c_i \geq \mu + t) &\leq \exp(\frac{-2t^2}{n}) \\
	 & = \exp(-2\log n) = n^{-2}
\end{split}
\end{equation*}

The first step holds since all $b_{i,j}$ are 0-1 variables. 
Next, the event $(\max_{1 \leq j \leq n}(c_j) \geq \mu + t)$ can be viewed as
$\cup_{c_i} (c_i \geq \mu + t )$, by Union Bound, the following holds:
\begin{equation*}
\begin{split}
	Pr(\Gamma \geq \mu + t) &=Pr(\max_{1\leq j \leq n}(c_j) \geq \mu + t)  \\
		& = Pr(\cup_{c_i} (c_i \geq \mu + t )) \\
		&\leq \Sigma_{1 \leq i \leq n} Pr(c_i \geq \mu + t) \\ 
		&= n^{-1} = 1/n
\end{split}
\end{equation*}
Substitute back $t$ and $\mu$, we achieve the following concise form:
\begin{equation*}
	Pr(\Gamma \geq (d/2 + \sqrt{n\log n})) \leq 1/n
\end{equation*}
This indicates the probability of $(\Gamma-d/2)$ being no greater than $ O(\sqrt{n\log n})$ is $(1-1/n)$. 
Since $\Gamma^* \geq d/2$, it follows with probability greater than $(1-1/n)$, 
the $\Gamma - \Gamma^*$ is no greater than $O(\sqrt{n\log n})$.
When the aggregated graph is \emph{dense} (i.e., $d\geq \sqrt{12 \log n}$),
the Chernoff Bound can be used to derive a tighter bound of 
$O(\sqrt{\log n}) $ following the similar reasoning.
\end{proof}

@@

\subsection{Proof of Theorem~\ref{THM:SPM_CORRECT}}
\label{apx:spm_correct}
\begin{proof}
For soundness, let $P$ be a pattern enumerated by SPARE. For any two objects $o_1, o_2 \in P.O$, the edge $e(o_1,o_2)$ is a superset of $P.T$. By the definition of star, $\forall t \in P.T, C_t(o_1) = C_t(o_2)$. As $P.T$ is a valid sequence, by the definition of GCMP, $P$ is a true pattern.
For completeness, let $P$ be a true pattern. Let $s$ be the object with smallest ID in $P.O$. We prove that $P$ must be output by Algorithm~\ref{algo:apriori_mining} form $Sr_s$. 
First, based on the definition of star, every object in $P.O$ appears in $Sr_s$. Since $P.T$ is decomposable, then by Lemma 3 $\forall O' \subseteq O$, the time sequence of $O'$ would not be eliminated by any $\mathtt{sim}$ operations.  Next, we prove at every iteration \emph{level} $\leq |P.O|$, $P.O \subset O_u$, where $O_u$ is the forward closure. We prove by induction. When $level$ = 2, it obviously holds. If $P.O \subset O_u$ at \emph{level $i$}, then any subsets of $P.O$ with size $i$ are in the candidate set. In \emph{level} $i+1$, these subsets are able to grow to a bigger subset (in last iteration, they grow to $P.O$). This suggests that no subsets are removed by Lines~\ref{code:output1-start}-\ref{code:output2-end}. Then, $P.O \subset U_{i+1}$ holds. In summary, $P.O$ does not pruned by simplification, monotonicity and forward closure, therefore $P$ must be returned by SPARE.
\end{proof}

>>>>

\subsection{Proofs of Theorem~\ref{THM:SPM_LB} and~\ref{THM:SPM_LB_INC}}
\label{apx:thm2proof}

\begin{proof}
$\Gamma$ can be formalized using linear algebra:
Let $G_A$ be an aggregated graph, with a $n \times n$ adjacent matrix $J$.
Since a vertex order is a permutation of $J$, the adjacent matrices 
of any reordered graphs can be represented as $PJP^T$
where $P \in \mathbb{P}$ is a $n\times n$ \emph{permutation matrix}~\footnote{an identity matrix with rows shuffled}.
In star partitioning, we assign each edge $e(i,j)$ in $G_A$ to the lower vertex, 
then the matrix $B=\triu(PJP^T)$~\footnote{\text{triu} is the upper triangle part of a matrix}
represents the assignment matrix wrt. $P$ (i.e., $b_{i,j} = 1$ if vertex $j$ is in star $Sr_i$).
Let vector $\vec{b}$ be the \textit{one}\footnote{every element in $\vec{b}$ is $1$} 
vector with size $n$. Let $\vec{c} = B\vec{b}$, then each $c_i$ 
denotes the number of edges in star $Sr_i$. Thus, $\Gamma$ can be represented
as the infinity norm of $B\vec{b}$. Let $\Gamma^*$ be the minimum $\Gamma$ among all vertex orderings, that is

@@

Let $B^*$ be the assignment matrix wrt. the optimal vertex ordering.
Since we have a star for each object, by the degree-sum formula and pigeon-hole theorem, 
$\Gamma^*=||B^*\vec{b}||_\infty \geq d/2$.
Next, for a vertex ordering $P$, let $e_{i,j}$ be an entry in $PAP^T$. Since 
edges in graph $G$ are independent, then $e_{i,j}$s are independent. 
Let $d_i$ denote the degree of vertex $i$, since a vertex ordering does not
affect the average degree,
then $E[d_i]=E[\Sigma_{1\leq j \leq n}e_{i,j}]=d$. Therefore, 
entries in $B$ can be written as :

@@

\begin{equation*}
\begin{split}
	Pr(c_i \geq \mu + t) &\leq \exp(\frac{-2t^2}{n}) = \exp(-2\log n) = n^{-2}
\end{split}
\end{equation*}

The first step holds since all $b_{i,j}$ are 0-1 variables. 
Next, the event $(\max_{1 \leq j \leq n}(c_j) \geq \mu + t)$ can be viewed as
$\cup_{c_i} (c_i \geq \mu + t )$, by Union Bound, the following holds:
\begin{equation*}
\begin{split}
	Pr(\Gamma \geq \mu + t) &=Pr(\max_{1\leq j \leq n}(c_j) \geq \mu + t)  \\
		& = Pr(\cup_{c_i} (c_i \geq \mu + t )) \\
		&\leq \Sigma_{1 \leq i \leq n} Pr(c_i \geq \mu + t) = n^{-1} = 1/n
\end{split}
\end{equation*}
Substitute back $t$ and $\mu$, we achieve the following concise form:
\begin{equation*}
	Pr(\Gamma \geq (d/2 + \sqrt{n\log n})) \leq 1/n
\end{equation*}
This indicates the probability of $(\Gamma-d/2)$ being no greater than $ O(\sqrt{n\log n})$ is $(1-1/n)$. 
Since $\Gamma^* \geq d/2$, it follows with probability greater than $(1-1/n)$, 
the $\Gamma - \Gamma^*$ is no greater than $O(\sqrt{n\log n})$.
When the aggregated graph is \emph{dense} (i.e., $d\geq \sqrt{12 \log n}$),
the Chernoff Bound can be used to derive a tighter bound of 
$O(\sqrt{\log n}) $ following the similar reasoning.
\end{proof}

@@

\subsection{Proof of Theorem~\ref{THM:SPM_CORRECT}}
\label{apx:spm_correct}
\begin{proof}
For soundness, let $P$ be a pattern enumerated by SPARE. For any two objects $o_1, o_2 \in P.O$, the edge $e(o_1,o_2)$ is a superset of $P.T$. By the definition of star, $o_1$ $o_2$ belong to the same cluster at every timestamps in $P.T$. As $P.T$ is a valid sequence, by the definition of GCMP, $P$ is a true pattern.
For completeness, let $P$ be a true pattern. Let $s$ be the object with smallest ID in $P.O$. We prove that $P$ must be output by Algorithm~\ref{algo:apriori_mining} form $Sr_s$. 
First, based on the definition of star, every object in $P.O$ appears in $Sr_s$. Since $P.T$ is decomposable, then by Lemma 3 $\forall O' \subseteq O$, the time sequence of $O'$ would not be eliminated by any $\mathtt{sim}$ operations.  Next, we prove at every iteration \emph{level} $\leq |P.O|$, $P.O \subset O_u$, where $O_u$ is the forward closure. We prove by induction. When $level$ = 2, it obviously holds. If $P.O \subset O_u$ at \emph{level $i$}, then any subsets of $P.O$ with size $i$ are in the candidate set. In \emph{level} $i+1$, these subsets are able to grow to a bigger subset (in last iteration, they grow to $P.O$). This suggests that no subsets are removed by Lines~\ref{code:output1-start}-\ref{code:output2-end}. Then, $P.O \subset U_{i+1}$ holds. In summary, $P.O$ does not pruned by simplification, monotonicity and forward closure, therefore $P$ must be returned by SPARE.
\end{proof}

### 2016-07-01 sec1_introduction.tex
Corrected several typos
Need to add authors and affliations
Final Version
Submitted to VLDB

A crucial task of data analysis on top of trajectories is 
to discover co-moving objects. A \emph{co-movement} pattern~\cite{li2013managing} 
refers to a group of objects traveling together for a certain period of time 
and the group is normally determined by their spatial proximity. 
A pattern is prominent if the size of the group exceeds $M$ and the length of the duration exceeds $K$, where $M$ and $K$ are parameters specified by users. Rooted from such a basic definition 
and driven by different mining applications, there are a bunch of variants 
of co-movement patterns that have been developed with more advanced constraints.

@@

\begin{figure}[h]
\centering
\includegraphics[width=0.4\textwidth]{related_work.eps}
\caption{Trajectories and co-movement patterns; The example consists of six trajectories across six snapshots. Objects in spatial clusters are enclosed by dotted circles. $M$ is the minimum cluster cardinality; $K$ denotes the minimum number of snapshots for the occurrence of a spatial cluster; and $L$ denotes the minimum length for local consecutiveness.}
\label{fig:related_work}
\end{figure}

@@

\begin{table} \scriptsize
\centering
\begin{tabular}{|c|l|c|l|}
\hline 
\textbf{Pattern} & {\tiny \textbf{Proximity}} & {\tiny \textbf{Consecutiveness}} & {\tiny \textbf{Time Complexity}}\\ 
\hline 
flock~\cite{gudmundsson2004flock} & disk-based &  global & {\tiny $O(|\mathbb{O}||\mathbb{T}|(M + \log(|\mathbb{O}|)))$} \\ 
\hline 
convoy~\cite{jeung2008convoy} & density-based &   global & {\tiny $O(|\mathbb{O}|^2+|\mathbb{O}||\mathbb{T}|)$}\\ 
\hline 
swarm~\cite{li2010swarm} & density-based  & - & {\tiny $O(2^{|\mathbb{O}|}|\mathbb{O}||\mathbb{T}|)$}  \\ 
\hline 
group~\cite{wang2006grouppattern} & disk-based &  local & {\tiny $O(|\mathbb{O}|^2|\mathbb{T}|)$}\\ 
\hline 
platoon~\cite{li2015platoon} & density-based &  local & {\tiny $O(2^{|\mathbb{O}|}|\mathbb{O}||\mathbb{T}|)$}\\ 
\hline 
\end{tabular} 
\caption{Constraints and complexity of co-movement patterns. The time complexity indicates the performance in the worst case, where $|\mathbb{O}|$ is the total number of objects, $|\mathbb{T}|$ is the number of descritized timestamps and $M$ is the minimum cluster cardinality. }
\label{tbl:existing_co_patterns}
\end{table}
The other issue with existing methods is that they are built on top of centralized indexes which may not be scalable. Table~\ref{tbl:existing_co_patterns} shows their theoretical complexities in the worst cases and the largest real dataset ever evaluated in previous studies is up to million-scale points collected from hundreds of moving objects. In practice, the dataset is of much higher scale and the scalability of existing methods is left unknown. Thus, we conduct an experimental evaluation with $4000$ objects moving for $2500$ timestamps to examine the scalability. Results in Figure~\ref{fig:related_work_scalability} show that their performances degrade dramatically as the dataset scales up. For instance, the detection time of \emph{group} drops twenty times as the number of objects grows from \emph{1k} to \emph{4k}. Similarly,
the performance of \emph{swarm} drops over fifteen times as the number of snapshots grows from \emph{1k} to \emph{2.5k}.
These observations imply that existing methods are not scalable to support large-scale trajectory databases.

\begin{figure}[h]
	\vspace{-3mm}
    \centering
    \begin{subfigure}[b]{0.23\textwidth}
            \centering
            \includegraphics[width=\textwidth]{rw_perf_O.eps}
		\subcaption{$1k$ timestamps vary $O$} 
    \label{fig:fig1}
    \end{subfigure}
    \begin{subfigure}[b]{0.23\textwidth}
            \centering
            \includegraphics[width=\textwidth]{rw_perf_T.eps}
         \subcaption{$1k$ objects vary $T$}
    \label{fig:fig2}
    \end{subfigure}
    \vspace{-2mm}
    \caption{Performance measures on existing co-movement patterns. A sampled Geolife dataset
    is used with up two 2.4 million data points. Default parameters are $M=15$ $K=180$ $L=30$.}
    \label{fig:related_work_scalability}
\end{figure}

Therefore, our primary contributions in this paper are to close these two gaps. 
First, we propose the \emph{general co-movement pattern} (GCMP) which models
various co-moment patterns in a unified way and can avoid 
the \emph{loose-connection} anomaly. In GCMP, we introduce a new gap parameter $G$ to pose a constraint on the temporal gap between two consecutive segments. By setting a feasible $G$, the loose-connection anomaly can be avoided. In addition, our GCMP is both general and expressive. It can be reduced to any of the previous patterns by customizing its parameters.

Second, we investigate deploying our GCMP detector on MapReduce platforms (such as Hadoop and Spark) to tackle the scalability issue. Our technical contributions are three-fold. First, we replicate the snapshots in multiple data chunks to support efficient parallel processing. Second, we devise a novel \emph{Star Partition and ApRiori Enumerator} (SPARE) framework as a fine-granularity partitioning strategy to achieve workload balance. For each star, an Apriori Enumerator is adopted to mine the co-movement patterns. Third, we leverage the \emph{temporal monotonicity} property of of GCMP 
to design several optimization techniques including \emph{sequence simplification}, \emph{monontonicity pruning} and \emph{forward closure check} to further reduce the number of candidates enumerated.

We conduct a set of extensive experiments on three large-scaled real datasets with hundreds of millions 
temporal points. 
The results show that both our parallel scheme efficiently supports GCMP mining in large datasets.
In particular, with near 200 million trajectory points, 
SPARE runs in 12 minutes using 162 cores, whereas
centralized solutions take from 10 to 30 hours.
Moreover, our optimized SPARE methods achieves upto 10 times efficiency
as compared to the baseline algorithm with almost linear scalability.

The rest of our paper is organized as follows: Section~\ref{sec:related_works} summarizes the relevant literature on 
trajectory pattern mining. Section~\ref{sec:definition} states the problem definition of our general co-movement pattern mining. Section~\ref{sec:trm} provides a baseline solution. An advanced solution named
\emph{Star Partition and ApRiori Enumerator} (SPARE) is presented in Section~\ref{sec:spm}. Section~\ref{sec:exp} conducts extensive experiments to verify the efficiency of our system. Finally Section~\ref{sec:concl} concludes the paper.

>>>>

A crucial task of data analysis on top of trajectories is 
to discover co-moving objects. A \emph{co-movement} pattern~\cite{li2013managing,zheng2015survey} 
refers to a group of objects traveling together for a certain period of time 
and the group is normally determined by their spatial proximity. 
A pattern is prominent if the size of the group exceeds $M$ and the length of the duration exceeds $K$, where $M$ and $K$ are parameters specified by users. Rooted from such a basic definition 
and driven by different mining applications, there are a bunch of variants 
of co-movement patterns that have been developed with more advanced constraints.

@@

\begin{figure}[h]
\centering
\includegraphics[width=0.45\textwidth]{related_work.eps}
\caption{Trajectories and co-movement patterns. The example consists of six trajectories across six snapshots. Objects in spatial clusters are enclosed by dotted circles. $M$ is the minimum cluster cardinality; $K$ denotes the minimum number of snapshots for the occurrence of a spatial cluster; and $L$ denotes the minimum length for local consecutiveness.}
\label{fig:related_work}
\end{figure}

@@

\begin{table} \scriptsize
\centering
\begin{tabular}{|l|l|c|l|}
\hline 
\textbf{Pattern} & {\tiny \textbf{Proximity}} & {\tiny \textbf{Consecutiveness}} & {\tiny \textbf{Time Complexity}}\\ 
\hline 
flock~\cite{gudmundsson2004flock} & disk-based &  global & {\tiny $O(|\mathbb{O}||\mathbb{T}|\log(|\mathbb{O}|))$} \\ 
\hline 
convoy~\cite{jeung2008convoy} & density-based &   global & {\tiny $O(|\mathbb{O}|^2+|\mathbb{O}||\mathbb{T}|)$}\\ 
\hline 
swarm~\cite{li2010swarm} & density-based  & - & {\tiny $O(2^{|\mathbb{O}|}|\mathbb{O}||\mathbb{T}|)$}  \\ 
\hline 
group~\cite{wang2006grouppattern} & disk-based &  local & {\tiny $O(|\mathbb{O}|^2|\mathbb{T}|)$}\\ 
\hline 
platoon~\cite{li2015platoon} & density-based &  local & {\tiny $O(2^{|\mathbb{O}|}|\mathbb{O}||\mathbb{T}|)$}\\ 
\hline 
\end{tabular} 
\caption{Constraints and complexities of co-movement patterns. The time complexity indicates the performance wrt.
$|\mathbb{O}|$, $|\mathbb{T}|$ in the worst case, where $|\mathbb{O}|$ is the number of objects, and $|\mathbb{T}|$ is the number of discretized timestamps.}
\label{tbl:existing_co_patterns}
\end{table}
The other issue with existing methods is that they are built on top of centralized indexes which may not be scalable. Table~\ref{tbl:existing_co_patterns} shows their theoretical complexities in the worst cases and the largest real dataset ever evaluated in previous studies is up to million-scale points collected from hundreds of moving objects. In practice, the dataset is of much higher scale and the scalability of existing methods is left unknown. Thus, we conduct an experimental evaluation with $4000$ objects moving for $2500$ timestamps to examine the scalability. Results in Figure~\ref{fig:related_work_scalability} show that their performances degrade dramatically as the dataset scales up. For instance, the detection time of \emph{group} drops twenty times as the number of objects grows from \emph{1k} to \emph{4k}. Similarly,
the performance of \emph{swarm} drops over fifteen times as the number of snapshots grows from \emph{1k} to \emph{2.5k}.
These observations imply that existing methods are not scalable to support large-scale trajectory databases.

\begin{figure}[h]
	\vspace{-3mm}
    \centering
    \begin{subfigure}[b]{0.23\textwidth}
            \centering
            \includegraphics[width=\textwidth]{rw_perf_O.eps}
		\subcaption{$1k$ timestamps vary $O$} 
    \label{fig:fig1}
    \end{subfigure}
    \begin{subfigure}[b]{0.23\textwidth}
            \centering
            \includegraphics[width=\textwidth]{rw_perf_T.eps}
         \subcaption{$1k$ objects vary $T$}
    \label{fig:fig2}
    \end{subfigure}
    \vspace{-2mm}
    \caption{Performance measures on existing co-movement patterns. A sampled GeoLife dataset
    is used with up two 2.4 million data points. Default parameters are $M=15$, $K=180$, $L=30$.}
    \label{fig:related_work_scalability}
\end{figure}

Therefore, our primary contributions in this paper are to close these two gaps. 
First, we propose the \emph{general co-movement pattern} (GCMP) which models
various co-moment patterns in a unified way and can avoid 
the \emph{loose-connection} anomaly. In GCMP, we introduce a new gap parameter $G$ to pose a constraint on the temporal gap between two consecutive segments. By setting a feasible $G$, the loose-connection anomaly can be effectively controlled. In addition, our GCMP is both general and expressive. It can be reduced to any of the previous patterns by customizing its parameters.

Second, we investigate deploying our GCMP detector on MapReduce platforms (such as Hadoop and Spark) to tackle the scalability issue. Our technical contributions are three-fold. First, we replicate the snapshots in multiple data chunks to support efficient parallel processing. Second, we devise a novel \emph{Star Partitioning and ApRiori Enumerator} (SPARE) framework as a fine-granularity partitioning strategy to achieve workload balance. For each star, an Apriori Enumerator is adopted to mine the co-movement patterns. Third, we leverage the \emph{temporal monotonicity} property of GCMP 
to design several optimization techniques including \emph{sequence simplification}, \emph{monotonicity pruning} and \emph{forward closure check} to further reduce the number of candidates enumerated.

We conduct a set of extensive experiments on three large-scaled real datasets with hundreds of millions of
temporal points. 
The results show that both our parallel scheme efficiently supports GCMP mining in large datasets.
In particular, with near 200 million trajectory points, 
SPARE runs in 12 minutes using 162 cores, whereas
centralized solutions take from 10 to 30 hours.
Moreover, our optimized SPARE methods achieves upto 14 times efficiency
as compared to the baseline algorithm with almost linear scalability.

The rest of our paper is organized as follows: Section~\ref{sec:related_works} summarizes the relevant literature on 
trajectory pattern mining. Section~\ref{sec:definition} defines the problem of general co-movement pattern mining. Section~\ref{sec:trm} provides a baseline solution. An advanced solution named
\emph{Star Partitioning and ApRiori Enumerator} (SPARE) is presented in Section~\ref{sec:spm}. Section~\ref{sec:exp} conducts extensive experiments to verify the efficiency of our solutions. Finally, Section~\ref{sec:concl} concludes the paper.

### 2016-07-01 sec3_definitions.tex
Final Version
Submitted to VLDB

\section{Definitions}
\label{sec:definition}
Let $\mathbb{O} = \{o_1 ,o_2,...,o_n\}$ be the set of objects and $\mathbb{T} =(1,2,...,N)$ be the discretized temporal dimension. A time sequence $T$ is defined as a ordered subset of $\mathbb{T}$. Given two time sequences $T_1$ and $T_2$, we define a bunch of commonly-used operators in this paper in Table~\ref{tbl:operators}.

@@

\begin{definition}[$G$-connected]
A time sequence $T$ is $G$-connected if the gap between any of its neighboring timestamps is no greater than $G$. That is
 $\forall i \in (1,...,|T|-1), T[i+1]-T[i] \leq G$.
\end{definition}

@@

Given a trajectory database that is discretized into snapshots, we can conduct a clustering method, either disk-based or density-based, to identify groups with spatial proximity. Let $T$ be the set of timestamps in which a group of objects $O$ are clustered. We are ready to define a more general co-movement pattern:
\begin{definition}[General Co-Movement Pattern]
A general co-movement pattern finds a set of objects $O$ satisfying the following five constraints: (1) \textbf{closeness:} the objects in $O$ belong to the same cluster in the timestamps of $T$; (2) \textbf{significance:} $|O| \geq M$; (3) \textbf{duration:} $|T| \geq K$; (4) \textbf{consecutiveness:} $T$ is $L$-consecutive; and (5) \textbf{connection:} $T$ is $G$-connected.
\end{definition}
There are four parameters in our general co-movement pattern, including object constraint $M$ and temporal constraints $K,L,G$.  By customizing these parameters, our pattern can 
express other patterns proposed in the previous literature, as illustrated in Table~\ref{tbl:patterns}. 
In particular, by setting $G=|\mathbb{T}|$, we achieve the \emph{platoon} pattern. By setting $G=|\mathbb{T}|,L=1$, we reach the \emph{swarm} pattern. By setting $G=|\mathbb{T}|$, $M=2$, $K=1$, we gain the \emph{group} pattern. Finally by setting $G=1$, we result in the \emph{convoy} and \emph{flock} patterns. 
In addition to the flexibility of representing other existing patterns, our GCMP is able to avoid the \emph{loose connection} anomaly by tuning the parameter $G$. 
It is notable that GCMP cannot be modeled by existing patterns. 
\begin{table}[h]
\centering
\begin{tabular}{|l|c|c|c|c|c|}
\hline 
\textbf{Pattern} & $M$ & $K$ & $L$ & $G$ & \textbf{Clustering} \\ 
\hline
Group & $2$ & $1$ & $2$ & $|\mathbb{T}|$ & Disk-based\\
\hline
Flock & $\cdot$ & $\cdot$ & $K$ & $1$ & Disk-based \\
\hline 
Convoy & $\cdot$ & $\cdot$ & $K$ & $1$ & Density-based\\ 
\hline 
Swarm & $\cdot$ & $\cdot$ & $1$ & $|\mathbb{T}|$ & Density-based \\ 
\hline 
Platoon & $\cdot$ & $\cdot$ & $\cdot$ & $|\mathbb{T}|$ & Density-based\\ 
\hline 
\end{tabular} 
\caption{Expressing other patterns using GCMP. $\cdot$ indicates a user specified value. $M$ represents the 
object \emph{size} constraint. $K$ represents the \emph{duration} constraint. $L$ represents the \emph{consecutiveness} constraint. $G$ represents the \emph{connection} constraint.}
\label{tbl:patterns}
\end{table}
\eat{ 
It is also observable that the number of patterns in GCMP could be exponential under some parameter settings (i.e., 
when expressing \emph{swarm}). In particular, given a parameter $M$, if a pattern $P$ is valid, then any subset of $P$ with 
size $M$ is also a valid pattern. This results in additional $\Sigma_{M\geq i \geq |P.O|} {|P.O| \choose i}$ patterns,
which is clearly overwhelming and redundant. For all these patterns, output $P$ is sufficient. Therefore, we define the \emph{Closed General Co-Movement Pattern} as follows:

\begin{definition}[Closed General Co-Movement Pattern]
A general co-moving pattern $P=\langle O:T \rangle$ is closed if and only if there does not exist another general co-moving pattern $P'$ s.t. $P.O \subseteq P'.O$.
\end{definition}

For example, let $M=2,K=2,,L=1,G=1$. In Figure~\ref{fig:related_work},
the pattern $P_1 = \{o_3,o_4:1,2,3\}$ is not a closed pattern. This is because $P_2=\{o_3,o_4,o_5:2,3\}$ is a closed pattern since $P_2.O \supset P_1.O$. The closed pattern avoids outputting duplicate information, thus making the result patterns more compact. 
}

Our definition of GCMP is independent of the clustering method. Users can apply different clustering methods to facilitate different application needs. 
We currently expose both disc-region based clustering and DBSCAN as options to the users. In summary, the goal of this paper is to present a parallel solution for discovering all the valid GCMPs from large-scale trajectory databases. Before we move on to the algorithmic part, we list the notations that are used in the following sections.

\begin{table}[h]\scriptsize
\centering
\begin{tabular}{|c|l|} 
\hline
\textbf{Symbol} & \textbf{Meaning} \\
\hline
$S_t$ & snapshot of objects at time $t$ \\
\hline
$M$ & significance constraint \\
\hline 
$K$ & duration constraint\\
\hline
$L$ & consecutiveness constraint\\
\hline
$G$ & connection constraint \\
\hline
$P=\langle O:T \rangle$ & pattern with object set $O$, time sequence $T$\\
\hline
$C_t(o)$ & cluster of object $o$ at time $t$ \\
\hline 
$S_t$ & set of clusters at time $t$\\
\hline 
$\lambda_t$ & partition with snapshots $S_t,..,S_{t+\eta-1}$ \\\hline
$\eta$ & replication factor in the TRPM framework\\
\hline
$Sr_i $ &  star partition for object $i$ \\
\hline 
$\Gamma$ & size of the largest star in star partition \\
\hline
\end{tabular} 
\caption{Summary of the use of notations.}
\end{table}

>>>>

\section{Definitions}
\label{sec:definition}
Let $\mathbb{O} = \{o_1 ,o_2,...,o_n\}$ be the set of objects and $\mathbb{T} =(1,2,...,N)$ be the discretized temporal dimension. A time sequence $T$ is defined as an ordered subset of $\mathbb{T}$. Given two time sequences $T_1$ and $T_2$, we define a bunch of commonly-used operators in this paper in Table~\ref{tbl:operators}.

@@

\begin{definition}[$G$-connected]
A time sequence $T$ is $G$-connected if the gap between any of its neighboring timestamps is no greater than $G$, i.e.,
 $\forall i \in (1,\ldots,|T|-1), T[i+1]-T[i] \leq G$.
\end{definition}

@@

Given a trajectory database that is discretized into snapshots, we can conduct a clustering method, either disk-based or density-based, to identify groups with spatial proximity. Let $T$ be the set of timestamps in which a group of objects $O$ are clustered. We are ready to define a more general co-movement pattern:
\begin{definition}[General Co-Movement Pattern]
A general co-movement pattern finds a set of objects $O$ satisfying the following five constraints: (1) \textbf{closeness:} the objects in $O$ belong to the same cluster in the timestamps of $T$; (2) \textbf{significance:} $|O| \geq M$; (3) \textbf{duration:} $|T| \geq K$; (4) \textbf{consecutiveness:} $T$ is $L$-consecutive; and (5) \textbf{connection:} $T$ is $G$-connected.
\end{definition}
There are four parameters in our general co-movement pattern, including object constraint $M$ and temporal constraints $K,L,G$.  By customizing these parameters, our pattern can 
express other patterns proposed in the previous literature, as illustrated in Table~\ref{tbl:patterns}. 
In particular, by setting $G=|\mathbb{T}|$, we achieve the \emph{platoon} pattern. By setting $G=|\mathbb{T}|,L=1$, we reach the \emph{swarm} pattern. By setting $G=|\mathbb{T}|$, $M=2$, $K=1$, we gain the \emph{group} pattern. Finally by setting $G=1$, we result in the \emph{convoy} and \emph{flock} patterns. 
In addition to the flexibility of representing other existing patterns, our GCMP is able to avoid the \emph{loose connection} anomaly by tuning the parameter $G$. 
It is notable that GCMP cannot be modeled by existing patterns. 
\begin{table}[h]
\centering
\begin{tabular}{|l|c|c|c|c|c|}
\hline 
\textbf{Pattern} & $M$ & $K$ & $L$ & $G$ & \textbf{Clustering} \\ 
\hline
Group & $2$ & $1$ & $2$ & $|\mathbb{T}|$ & Disk-based\\
\hline
Flock & $\cdot$ & $\cdot$ & $K$ & $1$ & Disk-based \\
\hline 
Convoy & $\cdot$ & $\cdot$ & $K$ & $1$ & Density-based\\ 
\hline 
Swarm & $\cdot$ & $\cdot$ & $1$ & $|\mathbb{T}|$ & Density-based \\ 
\hline 
Platoon & $\cdot$ & $\cdot$ & $\cdot$ & $|\mathbb{T}|$ & Density-based\\ 
\hline 
\end{tabular} 
\caption{Expressing other patterns using GCMP. $\cdot$ indicates a user specified value. $M$ represents the 
\emph{significance} constraint. $K$ represents the \emph{duration} constraint. $L$ represents the \emph{consecutiveness} constraint. $G$ represents the \emph{connection} constraint.}
\label{tbl:patterns}
\end{table}

Our definition of GCMP is independent of the clustering method. Users can apply different clustering methods to facilitate different application needs. 
We currently expose both disk-region based clustering and DBSCAN as options to the users. In summary, the goal of this paper is to present a parallel solution for discovering all the valid GCMPs from large-scale trajectory databases. Before we move on to the algorithmic part, we list the notations that are used in the following sections.

\begin{table}[h]\scriptsize
\centering
\begin{tabular}{|c|l|} 
\hline
\textbf{Symbol} & \textbf{Meaning} \\
\hline
$S_t$ & snapshot of objects at time $t$ \\
\hline
$M$ & significance constraint \\
\hline 
$K$ & duration constraint\\
\hline
$L$ & consecutiveness constraint\\
\hline
$G$ & connection constraint \\
\hline
$P=\langle O:T \rangle$ & pattern with object set $O$, time sequence $T$\\
\hline
%$C_t(o)$ & cluster of object $o$ at time $t$ \\
%\hline 
$S_t$ & set of clusters at snapshot $t$\\
\hline
$\eta$ & replication factor in the TRPM framework\\
\hline 
$\lambda_t$ & partition with snapshots $S_t,..,S_{t+\eta-1}$ \\
\hline
$G_A$ & aggregated graph in SPARE framework\\
\hline
$Sr_i $ &  star partition for object (vertex) $i$ \\
\hline 
$\Gamma$ & size of the largest star partition\\
\hline
\end{tabular} 
\caption{Summary of the use of notations.}
\end{table}
